### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsection{Target Applications}
While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks, we find many of those work targets on the encryption key on cryptography libraries. We find current side-channel attacks can be classified into the below three categories.

\subsubsection{Cryptography Libraries}

>>>>

\subsection{Target Applications}
While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks, we find many of those work targets on the encryption key on cryptography libraries. In general, current side-channel attacks can be classified into the below three categories.

\subsubsection{Cryptography Libraries}
The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. Many algorithms (Diffie-Helloman, RSA) implementations at that time use the simple modular exponentiation algorithm, which does not run in fixed time. By measuring the time differences between the  modular exponentiation algorithm computes the exponent bits (0 or 1), an attacker can recover the whole secret key bit by bit. Many well-known cryptography algorithms are vulnerable to side-channels.
